HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-02 paper/main.tex
Shortening the text

Human evaluation of machine translation normally uses sentence-level measures such as relative ranking
or adequacy/fluency scales. However these provide no insight into the MT errors,
and do not scale well with sentence length.
We argue for a semantics-based evaluation, which captures what meaning components
are retained in the MT output, providing a more fine-grained analysis of
translation quality, and enables the construction and tuning of semantics-based MT. 
We present a novel human semantic evaluation measure for MT, Human
UCCA-based MT Evaluation (HUME), building on the Universal Conceptual Cognitive Annotation (UCCA)
semantic representation scheme.
Making progress over previous work, the proposed measure takes into account
a wider range of semantic phenomena and does not rely on semantic annotation
of the MT output itself, whose interpretation is often unclear.
We experiment with four language pairs, demonstrating HUME's broad applicability,
as well as its reliability, reflected in its inter-annotator agreement rates and 
good correlation with human adequacy scores.

@@

We propose the HUME metric,
a human evaluation measure that decomposes over the UCCA semantic units of the sentence.
UCCA \parcite{abend2013universal} is an appealing candidate for semantic analysis,
due to its cross-linguistic applicability, support for rapid annotation, and coverage
of many fundamental semantic phenomena, such as verbal, nominal and adjectival
argument structures and their inter-relations.

HUME operates by aggregating human assessments of the translation quality of individual
semantic units in the source sentence. We 
%HUME only requires semantically annotating the source sentence,
are thus avoiding the semantic annotation of machine-generated text,
which is often garbled or semantically unclear.
This also allows the re-use of the source semantic annotation for
measuring the quality of different translations of the same source sentence,
and 
%By basing the measure on a direct comparison
%of the source and translation we avoid the difficulties created by using
avoids relying on possibly suboptimal reference translations,
albeit at the cost of requiring the
evaluator to be proficient in both the source and target languages.
%An elaborate comparison of HUME and HMEANT is given in \secref{sec:hmeant_comp}.

After a brief review (\secref{sec:background}), we describe HUME in detail
(\secref{sec:hume}).
Our experiments with four language pairs: English to Czech, German, Polish and Romanian (\secref{sec:experiments})
document HUME's inter-annotator agreement and efficiency (time of annotation). 
We further empirically compare HUME with direct assessment of human adequacy ratings,
and conclude by discussing the differences with HMEANT (\secref{sec:hmeant_comp}).

@@

\paragraph{MT Evaluation.}
%MT evaluation has been traditionally pursued through human-based
%evaluation that quantifies the adequacy of the translation in preserving the meaning 
%of the source sentence, and its fluency as a sentence in the target language
%\parcite{lopez2008statistical}.
Human evaluation is generally done by ranking the outputs of multiple systems
e.g., in the WMT tasks \parcite{bojar2015findings}, or by giving
adequacy/fluency scores to each translation, a procedure recently improved
by \perscite{graham2015improving}.
However, while providing the gold standard for MT evaluation, human evaluation
is not a scalable solution.
%and is infeasible where a wide variety of systems or parameter settings are to be evaluated.
% has motivated the construction of cheaper methods that correlate with human
%judgement.

@@

Structural units have sub-units (children in the UCCA graph), which may themselves
either be atomic or structural.
% Ondrej thinks the following can be simply removed:
%The labels assigned to such nodes reflect the extent to which
%the relation between the sub-units is preserved in $t$.
%\XXX{(BH: don't follow this) For instance, a Scene unit represents the relation between the
%Scene elements, such as the predicate (main relation), participants and adverbials.}
Structural units are labeled as ``Adequate'' or ``Bad'', meaning
that the relation between the sub-units went wrong\footnote{
  Three labels are used with atomic units, as opposed to two labels with structural units,
as atomic units are more susceptible to slight errors.}.
There are three major cases where the relationship between the children might go
wrong in translation.
First, the components of the translation may be ordered differently from the source,
such that the relation between them changes. For instance, if
the sentence ``man bites dog'' is translated into a sentence meaning ``dog bites man'',
the semantic unit corresponding to the Scene will be marked as Bad, while
the individual atomic units ``dog'', ``bites'' and ``man'' will be marked as Green.
Second, A superfluous word or phrase may be inserted into
the translation. For instance, if ``dog bites man'' is translated into ``dog viciously bites man''.
Third, one of the sub-units may be missing from the translation.
For instance, if ``dog bites man'' is translated into ``dog bites''.

@@

\begin{figure}[t]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{c}
\subfloat[English-German]{
  \iaafig{de}
}
\\
\subfloat[English-Romanian]{
  \iaafig{ro}
}
\end{tabular}
\caption{HUME vs DA scores. DA score have been standardised for each crowdsourcing annotator and averaged across exactly 10 annotators. HUME scores are averaged where there were two annotations. 
%The regression is calculated using linear least squares.
}
\label{fig:dacorrelation}
\end{figure}
Recent research~\cite{graham2015accurate,graham2015crowd} has proposed a new approach for collecting 
accuracy ratings, direct assessment (DA). By crowdsourcing a large number of adequacy judgements for each candidate 
translation on a fine-grained 
scale of 0 to 100, we can apply statistical measures which result in reliable aggregate scores. 
It has been shown that mean DA judgements correlate very strongly with each other. 
We followed~\parcite{graham2015accurate} and collected up to 15 adequacy judgements on most of the
HUME annotated translations for German and Romanian. To ensure high quality judgments
we restricted the IP of the annotators to those of the relevant country. We found that there were too
few Czech and Polish annotators, and removing the IP restriction led to very poor quality results.

@@

In Figure~\ref{fig:dacorrelationtypes} we can see an analysis of HUME correlations with DA by HUME node type. We can see that correlation increases when combining different sematic node types and that correlation is highest for node type ``all''. Some types of nodes seem to predict the DA scores better than others. The HUME scores on parallel scene nodes (H) and participant nodes (A) seem to correlate more strongly with DA than scores on process and state nodes (P+S) or linker nodes (L). Center nodes (C) are also more correlated than elaborator nodes (E), which is what we would expect given that center nodes are by definition more important to the semantics of a sentence than elaborators.

>>>>

Human evaluation of machine translation normally uses sentence-level measures such as relative ranking
or adequacy/fluency scales. However these provide no insight into possible errors,
and do not scale well with sentence length.
We argue for a semantics-based evaluation, which captures what meaning components
are retained in the MT output, providing a more fine-grained analysis of
translation quality, and enables the construction and tuning of semantics-based MT. 
We present a novel human semantic evaluation measure, Human
UCCA-based MT Evaluation (HUME), building on the Universal Conceptual Cognitive Annotation (UCCA)
semantic representation scheme.
%Making progress over previous work, the proposed measure takes into account
HUME covers
a wider range of semantic phenomena than previous methods and does not rely on semantic annotation
of the potentially garbled MT output. 
%itself, whose interpretation is often unclear.
We experiment with four language pairs, demonstrating HUME's broad applicability,
and report good
%as well as its reliability, reflected in its 
inter-annotator agreement rates and 
 correlation with human adequacy scores.

@@

We propose the HUME metric,
a human evaluation measure that decomposes over the UCCA semantic units.
% of the sentence.
UCCA \parcite{abend2013universal} is an appealing candidate for semantic analysis,
due to its cross-linguistic applicability, support for rapid annotation, and coverage
of many fundamental semantic phenomena, such as verbal, nominal and adjectival
argument structures and their inter-relations.

HUME operates by aggregating human assessments of the translation quality of individual
semantic units in the source sentence. We 
%HUME only requires semantically annotating the source sentence,
are thus avoiding the semantic annotation of machine-generated text,
which is often garbled or semantically unclear.
This also allows the re-use of the source semantic annotation for
measuring the quality of different translations of the same source sentence,
and 
%By basing the measure on a direct comparison
%of the source and translation we avoid the difficulties created by using
avoids relying on possibly suboptimal reference translations.
%albeit at the cost of requiring the
%evaluator to be proficient in both the source and target languages.
%An elaborate comparison of HUME and HMEANT is given in \secref{sec:hmeant_comp}.

%Could reinstate
%After a brief review (\secref{sec:background}), we describe HUME in detail
%(\secref{sec:hume}).
%Our experiments with four language pairs: English to Czech, German, Polish and Romanian (\secref{sec:experiments})
%document HUME's inter-annotator agreement and efficiency (time of annotation). 
%We further empirically compare HUME with direct assessment of human adequacy ratings,
%and conclude by discussing the differences with HMEANT (\secref{sec:hmeant_comp}).

@@

\paragraph{MT Evaluation.}
%MT evaluation has been traditionally pursued through human-based
%evaluation that quantifies the adequacy of the translation in preserving the meaning 
%of the source sentence, and its fluency as a sentence in the target language
%\parcite{lopez2008statistical}.
Human evaluation is generally done by ranking the outputs of multiple systems
e.g., in the WMT tasks \parcite{bojar2015findings}, or by giving
adequacy/fluency scores to each translation, a procedure recently improved
by \perscite{graham2015accurate}.
However, while providing the gold standard for MT evaluation, human evaluation
is not a scalable solution.
%and is infeasible where a wide variety of systems or parameter settings are to be evaluated.
% has motivated the construction of cheaper methods that correlate with human
%judgement.

@@

Structural units have sub-units (children in the UCCA graph), which may themselves
either be atomic or structural.
% Ondrej thinks the following can be simply removed:
%The labels assigned to such nodes reflect the extent to which
%the relation between the sub-units is preserved in $t$.
%\XXX{(BH: don't follow this) For instance, a Scene unit represents the relation between the
%Scene elements, such as the predicate (main relation), participants and adverbials.}
Structural units are labeled as ``Adequate'' or ``Bad'', meaning
that the relation between the sub-units went wrong\footnote{
  Three labels are used with atomic units, as opposed to two labels with structural units,
as atomic units are more susceptible to slight errors.}.
%here are three major cases where the relationship between the children might go
%wrong in translation and 
We will use the example ``man bites dog'' to illustrate typical examples of why a structural node
should be labelled as ``Bad'':
incorrect ordering (``dog bites man''), 
deletion (``man bites'') and insertion (``man bites biscuit dog''). 
%First, the components of the translation may be ordered differently from the source,
%such that the relation between them changes. For instance, if
%the sentence ``man bites dog'' is translated into a sentence meaning ``dog bites man'',
%the semantic unit corresponding to the Scene will be marked as Bad, while
%the individual atomic units ``dog'', ``bites'' and ``man'' will be marked as Green.
%Second, A superfluous word or phrase may be inserted into
%the translation. For instance, if ``dog bites man'' is translated into ``dog viciously bites man''.
%Third, one of the sub-units may be missing from the translation.
%For instance, if ``dog bites man'' is translated into ``dog bites''.

@@

\begin{figure}[t]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{c}
\subfloat[English-German]{
  \iaafig{de}
}
\\
\subfloat[English-Romanian]{
  \iaafig{ro}
}
\end{tabular}
\caption{HUME vs DA scores. DA score have been standardised for each crowdsourcing annotator and averaged across exactly 10 annotators. HUME scores are averaged where there were two annotations. 
%The regression is calculated using linear least squares.
}
\label{fig:dacorrelation}
\end{figure}
Recent research~\cite{graham2015accurate,graham2015crowd,graham2015improving} has proposed a new approach for collecting 
accuracy ratings, direct assessment (DA). By crowdsourcing a large number of adequacy judgements for each candidate 
translation on a fine-grained 
scale of 0 to 100, we can apply statistical measures which result in reliable aggregate scores. 
It has been shown that mean DA judgements correlate very strongly with each other. 
We followed~\parcite{graham2015accurate} and collected up to 15 adequacy judgements on most of the
HUME annotated translations for German and Romanian. To ensure high quality judgments
we restricted the IP of the annotators to those of the relevant country. We found that there were too
few Czech and Polish annotators, and removing the IP restriction led to very poor quality results.

@@

In Figure~\ref{fig:dacorrelationtypes} we can see an analysis of HUME correlations with DA by HUME node type. We can see that correlation increases when combining different sematic node types and that correlation is highest for node type ``all''. Some types of nodes seem to predict the DA scores better than others. The HUME scores on parallel scene nodes (H) and participant nodes (A) seem to correlate more strongly with DA than scores on process and state nodes (P+S) or linker nodes (L). Center nodes (C) are also more correlated than elaborator nodes (E), which is what we would expect given that center nodes are by definition more important to the semantics of a sentence than elaborators. We leave it to future work to construct a HUME score which weights the different node types according to their semantic relevance.
